\section{Brief Research Plan}
\label{sec:timetable}
~~~~The mile stones and allocated time consumption is planed as:
\begin{itemize}
\item
\textbf{Task 1.1}~Modelling the multiple tasks problem for data centres considering energy consumption and physics recourse management. (Month 1 to Month 6 with literature review)
\item
\textbf{Task 1.2}~To develop an adaptive accurate predition of work load in data centres based on a machine learning algorithm in Linux based data centre systems. The work needs to be conducted with sufficient data and the prediction method is expected to be tested in simulation and real circumstances (The cooperation between companies or data centres is needed). (Month 4 to Month 12)
\item
\textbf{Task 2.1}~Study around the machine learning algorithms \cite{ma}, including reinforcement learning and supervised learning, to identify an adaptive optimal task-resource scheduling approach. Develop the algorithms and examininf the performance in simulation, based on real time data in Linux. (Month 13 to Month 17 with literature review)
\item
\textbf{Task 2.2}~Investigate around different scheduling approaches, including game theory or queuing theory. Evaluation is needed for task scheduling in real data centres applications. Apply the proposed scheduling approach on real systems. There is always a ”gap” between theoretical design and actual performance cooperation between data centres or product companies is highly expected. (Month 16 to Month 25)
\item
\textbf{Task 3.1}~Study the trade-off between ease of programming and flexibilities of the abstractions. In Jikes RVM environment, I will develop an approach for flexible language abstractions using compiler frameworks, like OpenCL and EPL. (Month 25 to Month 29 with literature work)
\item
\textbf{Task 3.2}~Develop a dynamic energy-aware recompiler based on the proposed smart scheduler. Then the whole energy-efficient approach (all three Themes) for data centres will be assembled. The performance of the proposed tool-chain will be tested and evaluated. (Month 30 to Month 36) 
\item
\textbf{Thesis}~Conduct all finished work, push forward for possible improvements. Prepare and write up the thesis. (Month 37 to Month 42)
\end{itemize}
